Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure

### 2017-03-08 documents/TriangleScenarioArXiv/ts.tex
typo in abstract

\begin{document}
    \title{Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure}
    \author{Thomas C. Fraser}
    \email{tcfraser@tcfraser.com}
    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada \\ University of Waterloo, Waterloo, Ontario, Canada}
    % \author{Elie Wolfe}
    % \email{ewolfe@perimeter@institute.ca}
    % \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada}
    \date{\today}
    \begin{abstract}
        It has long been recognized that certain quantum correlations are often incompatible with particular assumption about classical causal structure. Such correlations are sometimes termed nonlocal, although they are more accurately termed non-classical, as the presence of correlations certifies the genuinely non-classical nature of a causal setup in a device-independent fashion.  Whenever a quantum correlation violates a causal compatibility inequality (e.g. a Bell inequality) then the correlation is witnessed as non-classical. Any constraint which is satisfied by all correlations which \textit{are} classically compatible with a given causal scenario defined a causal compatibility criterion. Such criteria were recently were recently derived for the Triangle structure [\href[pdfnewwindow]{http://arxiv.org/abs/1609.00672}{arXiv:1609.00672}] in the form of polynomial inequalities, begging the question: do any of those inequalities admit violation by quantum correlations? Numerical investigation suggests not, and we further conjecture that the set of correlations admitted by the classical Triangle structure is equivalent to the set of correlations admitted by its quantum generalization whenever the three observable variables are binary. Our main contribution in this work, however, is the derivation of new causal compatibility inequalities for the Triangle structure which \textit{do} admit quantum violation. We conclude by considering the possibility of quantum resources potentially qualitatively different from those known previously.
    \end{abstract}
    \maketitle
    \tableofcontents
    \setlength{\parskip}{1em}
    \clearpage

>>>>

\begin{document}
    \title{Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure}
    \author{Thomas C. Fraser}
    \email{tcfraser@tcfraser.com}
    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada \\ University of Waterloo, Waterloo, Ontario, Canada}
    % \author{Elie Wolfe}
    % \email{ewolfe@perimeter@institute.ca}
    % \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada}
    \date{\today}
    \begin{abstract}
        It has long been recognized that certain quantum correlations are often incompatible with particular assumption about classical causal structure. Such correlations are sometimes termed nonlocal, although they are more accurately termed non-classical, as the presence of correlations certifies the genuinely non-classical nature of a causal setup in a device-independent fashion.  Whenever a quantum correlation violates a causal compatibility inequality (e.g. a Bell inequality) then the correlation is witnessed as non-classical. Any constraint which is satisfied by all correlations which \textit{are} classically compatible with a given causal scenario defines a causal compatibility criterion. Such criteria were recently were recently derived for the Triangle structure [\href[pdfnewwindow]{http://arxiv.org/abs/1609.00672}{arXiv:1609.00672}] in the form of polynomial inequalities, begging the question: do any of those inequalities admit violation by quantum correlations? Numerical investigation suggests not, and we further conjecture that the set of correlations admitted by the classical Triangle structure is equivalent to the set of correlations admitted by its quantum generalization whenever the three observable variables are binary. Our main contribution in this work, however, is the derivation of new causal compatibility inequalities for the Triangle structure which \textit{do} admit quantum violation. We conclude by considering the possibility of quantum resources potentially qualitatively different from those known previously.
    \end{abstract}
    \maketitle
    \tableofcontents
    \setlength{\parskip}{1em}
    \clearpage
